QPLIB: A Library of Quadratic Programming Instances

### 2018-08-10 QPLIB-2.2.tex
reduce references to common structures

This description is deliberately coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flows \cite{FrFG16,FrGaSc14,FrGaSt16a,FGGP11,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FrGo13b,FGGP11}, and semi-continuous variables \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe06a,FrGe07a,FrGe09a,FGGP11}
\todo{SV: reduce to 1-3 citations here},
or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe09a,FGGP11}
\todo{SV: reduce to 1-3 citations here}.

>>>>

This description is deliberately coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flows \cite{FrFG16,FrGaSc14,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FGGP11}, and semi-continuous variables \cite{FrGaSc14,FrGaSt16a,FGGP11},
or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrGaSt16a,FrGe09a,FGGP11}.
